Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-08-12 supplement.tex
paragraph on TSI

\subsection{Validations using alternative data sets and model specification}

@@

>>>>

\subsection{Validations using alternative data sets and model specification}
\label{sec:validation-data-models}

@@

Across all validations to alternative datasets described in this section, model
fits were largely robust and matched those shown in the main text
(Figure~\ref{fig:best-fit-models})---the single outlier in these validations
was the continuous migration model fit to the dataset that included TSI instead
of GBR. The continuous migration model did not provide the best log-likelihood
among tested models, and our original model using the dataset with GBR
underestimated both $\sigma_{Dz}$ and $\sigma_{\pi_2}$ compared to data
(Figure~\ref{fig:supp-continuous-migration-fits}). In fitting this same model
to the TSI, the model provided a better fit to the $\sigma_{Dz}$ statistics but
a worse fit to the $\sigma_{\pi_2}$ statistics (and still provided a
significantly worse fit to the data compared to the multiple merger model).
These differences are likely driven by a combination of factors: the continuous
migration model mis-specifies historical dynamics in the range of 100-200ka;
the TSI are an inappropriate proxy for recent European admixture in East and
South Africa; and the TSI may also carry recent North African ancestry, which
is not captured in our model. Together, this highlights the sensitivity of
complex demographic inference to the choices of populations to include, as well
as to choices of model specification.
\aprcomment{not sure about these last two sentences}
